TBD

### 2021-02-16 outputs/paper/paper.Rmd
Graphs for all but Qs 5, 6, 11, 13
Some I want to modify to line graphs still to better illustrate the differences, e.g., in Q8 and Q9. Think the others that I left should also be line/scatter plots with best fit lines to display differences between control + treatment groups.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)
```

```{r, include=FALSE}
#### Global Functions ####
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}
```

@@

```{r, echo = FALSE}
#### Pie Chart ####
### Import cleaned business licences dataset
dfCleanBiz <- readr::read_csv("../../inputs/data/clean_business_licences.csv")
### Create data frame
dfBoroughs <- data.frame(
  group = dfCleanBiz$fsa,
  value = dfCleanBiz$n
)
### Calculate percentages
dfBoroughs <- dfBoroughs %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(dfBoroughs$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  arrange(desc(prop))
# print(dfBoroughs)
### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() + 
  geom_text(aes(y = ypos, label = percent(prop)), color = "white", size=3) +
  scale_fill_brewer(palette = "Paired")
```

```{r, echo = FALSE}

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(janitor)

all_simulated_dataset <- 
  readr::read_csv("../../inputs/data/simulated_data.csv")
control_group <-
  readr::read_csv("../../inputs/data/simulated_data.csv") %>%
  filter(type == "Control")
treatment_group <-
  readr::read_csv("../../inputs/data/simulated_data.csv") %>%
  filter(type == "Treated")
```

```{r, echo = FALSE, include=FALSE, message = FALSE}
#### Global Functions ####
percent <- function(x, decimal = 2, format = "f") {   
  paste0(formatC(x, format = format, digits = decimal), "%")
}
```

@@

```{r Q1, echo = FALSE, message = FALSE}
#### Pie Chart ####
### Import cleaned business licences dataset
dfCleanBiz <- readr::read_csv("../../inputs/data/clean_business_licences.csv")
### Create data frame
dfBoroughs <- data.frame(
  group = dfCleanBiz$fsa,
  value = dfCleanBiz$n
)
### Calculate percentages
dfBoroughs <- dfBoroughs %>% 
  arrange(desc(group)) %>%
  mutate(prop = value / sum(dfBoroughs$value) *100) %>%
  mutate(ypos = cumsum(prop)- 0.5*prop ) %>%
  arrange(desc(prop))
# print(dfBoroughs)
### Create pie chart
ggplot(dfBoroughs, aes(x="", y = prop, fill = group)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  coord_polar("y", start = 0) +
  theme_void() + 
  geom_text(aes(y = ypos, label = percent(prop)), color = "white", size=3) +
  scale_fill_brewer(palette = "Paired")
```

```{r Q2, echo = FALSE, message = FALSE}
### "What best describes the scale of your restaurant?
### Small (full seating capacity is under 30)
### Medium (full seating capacity between 30 and 60)
### Large (full seating capacity is 60+) "

ggplot(data = all_simulated_dataset, mapping = aes (x = Q2)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Small", "Medium", "Large")) +
  labs(x = "Scale of Restaurant",
       y = "# of Restaurants",
       title = "Q2") +
  theme_minimal()

```{r Q3, echo = FALSE, message = FALSE}
### What best describes your restaurant segmentation?
### Fast-food/quick service
### Casual Dining
### Fine Dining
### Other

ggplot(data = all_simulated_dataset, mapping = aes (x = Q3)) +
  geom_bar() +
  scale_x_discrete(limit = c ("Fine Dining", "Casual Dining", "Fast-food/quick service", "Other")) +
  labs(x = "Type of Restaurant",
       y = "# of Restaurants",
       title = "Q3") +
  theme_minimal()

```{r Q4, echo = FALSE, message = FALSE}
### How many years has your restaurant been in operation?
### 1-4 years
### 5-7 years
### 8-10 years
### 10 or more years

ggplot(data = all_simulated_dataset, mapping = aes (x = Q4)) +
  geom_bar() + coord_flip() +
  scale_x_discrete(limit = c ("1-4 years", "5-7 years", "8-10 years", "10 or more years")) +
  labs(x = "Years of Operation",
       y = "# of Restaurants",
       title = "Q4") +
  theme_minimal()

```{r Q5, echo = FALSE, message = FALSE}
### How many people do you currently employ?
### Prior to (intervention start date), how many people did you employ?
### Control

### line graph

```{r Q6, echo = FALSE, message = FALSE}
### How many people do you currently employ?
### Prior to (intervention start date), how many people did you employ?
### Treated

### line graph

```{r Q7, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) was your total sales revenue higher, lower, or about the same as it was ### during the same length of time last month.**
### Higher
### Lower
### Around the Same

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar(position = position_dodge(1)) +
  labs(x = "X",
       y = "Y",
       title = "Q7",
       fill = "Type") +
  theme_minimal()

```{r Q8, echo = FALSE, message = FALSE}
### What was the approximate percentage decrease in total sales revenue between (start date of intervention) and (end date of intervention) 
### compared to the same time period last year. **
### Decline of 50% or more
### Decline of 25% to 50%
### Decline of 10% to 25%
### Decline of 10% or less

ggplot(data = all_simulated_dataset, mapping = aes (x = Q8, fill = type)) +
  geom_bar(position = position_dodge(1)) + coord_flip() +
  scale_x_discrete(limit = c("Decline of 50% or more", "Decline of 25% to 50%", "Decline of 10% to 25%", "Decline of 10% or less")) + 
  labs(x = "Aprrox. Decrease in Total Sales Revenue",
       y = "# of Restaurants",
       title = "Q8",
       fill = "Type") +
  theme_minimal()

### make this a line graph

```{r Q9, echo = FALSE, message = FALSE}
### Before the (intervention start date), approximately how much of your total monthly sales revenue came from takeout or delivery?
### Did not offer takeout or delivery
### 15% or less
### 15-30%
### 30-50%
### 50-75%
### 75% or more

ggplot(data = all_simulated_dataset, mapping = aes (x = Q9, fill = type)) +
  geom_bar(position = position_dodge(1)) +  coord_flip() + 
  scale_x_discrete(limit = c("Did not offer takeout or delivery", "15% or less", "15-30%", "30-50%", "50-75%", "75% or more")) + 
  labs(x = "Total Monthly Sales Revenue Fromt Takeout or Delivery",
       y = "# of Restaurants",
       title = "Q9",
       fill = "Legend") +
  theme_minimal()

### make this a line graph instead
```

```{r Q10, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), did you make any adjustments to your menu prices?
### Yes, prices were raised
### Yes, prices were lowered
### No changes were made

ggplot(data = all_simulated_dataset, mapping = aes (x = Q10, fill = type)) +
  geom_bar(position = position_dodge(1)) +  coord_flip() + 
  scale_x_discrete(limit = c("Yes, prices were raised", "Yes, prices were lowered", "No changes were made")) + 
  labs(x = "Adjustments to Menu Prices",
       y = "# of Restaurants",
       title = "Q10",
       fill = "Legend") +
  theme_minimal()

```{r Q11, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention), which food courier service did you receive the most orders from?
### UberEats
### SkiptheDishes 
### DoorDash
### Other
### In-house delivery service
### None

```{r Q12, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce your ### restaurant’s hours of operation?
### Yes
### No

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "X",
       y = "Y",
       title = "Q12",
       fill = "Legend") +
  theme_minimal()

```{r Q13, echo = FALSE, message = FALSE}
### If yes, approximately how many hours per week did you reduce by
### 15% or less
### 15-30%
### 30-50%
### 50-75%
### 75% or more

### line graph

```{r Q14, echo = FALSE, message = FALSE}
### Between (start date of intervention) and (end date of intervention) did you reduce the 
### number of days your restaurant was open to the public?
### Yes
### No

ggplot(data = all_simulated_dataset, mapping = aes(x = Q14, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did you reduce the # of days you were open to the public between (start date) and (end date)?",
       y = "Y",
       title = "Q14",
       fill = "Legend") +
  theme_minimal()

```{r Q15, echo = FALSE, message = FALSE}
### If yes, how many days per week did you reduce by?
### 1-2 days
### 3-4 days
### 5-6 days
### 7 days
### Not Applicable

### bar graph/pie chart/line

ggplot(data = all_simulated_dataset, mapping = aes(x = Q15, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "How many days per week did you reduce by?",
       y = "# of restaurants",
       title = "Q15",
       fill = "Legend") +
  theme_minimal()
